
Loading the required Libraries

```{r}
library(dplyr)
library(ggplot2)
library(rjson)
library(jsonlite)
library(leaflet)
library(RCurl)
library(readr)
library(plotly)
```


#Choose the dataset named 'Data_Level3_MWCOG_RegionalTrafficCount.csv' under Data/
```{r}
TrafficCount <- read.csv(file.choose(), header=T)
```


#First plot for COUNTY vs TotVol
```{r}
plot <- TrafficCount %>% 
  group_by(COUNTY) %>%
  summarise(GroupedVolume = sum(TotVol)) %>%
  ggplot(aes(x = COUNTY, y = GroupedVolume, fill = COUNTY)) + 
  geom_bar(stat = 'identity')

ggplotly(plot)
```

Adding a DIR variable from the ABPair

```{r}
TrafficCount$Sta_Dir <- as.character(TrafficCount$Sta_Dir)
TrafficCount$DIR <- substring(TrafficCount$Sta_Dir, nchar(TrafficCount$Sta_Dir))
```

Checking if there is directional traffic in PG MALL
```{r}
DirPlot <- TrafficCount %>% 
  filter(COUNTY == "Prince George's County") %>%
  group_by(DIR) %>% 
  summarise(GroupedVolume = sum(TotVol)) %>% 
  ggplot(aes(x = DIR, y = GroupedVolume, fill = DIR)) + 
  geom_bar(stat = "identity")

ggplotly(DirPlot)
```

We can see that there are more vehicles going in the N/S directions.
Applying that to the whole dataset.
```{r}
DirPlot <- TrafficCount %>% group_by(DIR) %>% 
  summarise(GroupedVolume  = sum(TotVol)) %>%
  ggplot(aes(x = DIR, y = GroupedVolume, fill = DIR)) + geom_bar(stat = "identity")

ggplotly(DirPlot)
```

Most of the traffic is commuting from North to south and vice versa.

```{r}
DCTraffic <- TrafficCount %>%
  filter(COUNTY == 'District of Columbia')

mapOne <- leaflet(DCTraffic) %>% 
  addTiles()  %>% 
  addMarkers(lat = DCTraffic$YCOORD , lng = DCTraffic$XCOORD, label = DCTraffic$TotVol)
mapOne
```

The leaflet Map shows high traffic on the borders of the county because of interstate highway traffic.

Plot comparing various traffic types
```{r}
plot <- TrafficCount %>%
  ggplot(aes(x = PassCars + Motorcycles, y = AllTrucks)) + geom_point()

ggplotly(plot)
```


The leaflet Map shows high traffic on the borders of the county because of interstate highway traffic.

Next Part of the analysis. How does publc transport affect the traffic in the region.

```{r}
RegressionWithMetroLocations <- lm(TotVol~ nearest_metro_distance, data= DistanceStations)
summary(RegressionWithMetroLocations)
```

The regression output shows that the metro distance is inversely propotional to the traffic volume. Which suggests
[1] Metros are located in places of high economic activity hence people commute to those places. 
[2] Metro is not convenient for long commute.



